Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

\section{Conclusions}
The BGNN project demonstrates a clear need for improved metadata associated with specimen image collections. Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited. Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.

In this paper we presented such a metadata generation program. Using machine learning and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy. It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information. Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data. Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
\subsection{Future Work}
The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask. A deficiency of the current process is that it only operates on single channel intensity. Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background. Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features. Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.

@@

\section*{Acknowledgment}
%can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]

>>>>

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, particularly pixel analysis to improve and enrich metadata that enables researchers to apply machine learning to investigate scientific research questions on a scale that has never been pursued before. Our investigation focused on fish in general. Fish are vertebrate animals (phylum Chordata), with current knowledge of there being over 34,000 fish species\cite{fishbase}, and this figure does not include the world of unidentified species. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype. The ability to analyze thousands of images of of a single fish species computationally can lead to new discoveries that are impossible to manually pursue. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity. Efforts to integrate such methods in digital libraries, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes. Object detection as explored in our research, working with existing software, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.

Digital libraries serve to collect, provide access to, and archive rich collections, of a wide array of materials. Many digital libraries interconnect with open repository, supporting FAIR (Findable, Accessible, Interoperable, and Reuseable)\cite{wilkinson2016fair}. In discussing the future of digitial library services \cite{fox2021building} underscores the need to prepare for and test AI applications. The work presented here, with BGNN project demonstrates a clear need for improved metadata associated with specimen image collections. Much effort, time and money have been put into photographing and digitizing physical specimen, but without detailed and complete metadata properties the utility of these repositories for advanced computation analysis and machine learning is limited. Since it is prohibitively time intensive to generate all the pertinent properties by hand, automated techniques are needed to generate this missing metadata at scale.

\section{Conclusion}
In this paper we presented such a metadata generation program. Using machine learning and image informatics tools and techniques, it is able to locate, bitmask and analyze specimen (currently limited to fish) in collection images with a high degree of accuracy. It produces 6 of the 22 core BGNN metadata properties~\cite{leipzig2021biodiversity}, as well as image contrast, bounding boxes and scale and length information. Testing this program on \(7,244\) images from the INHS dataset~\cite{INHS}, we see that the vast majority of the resulting metadata is correct within a tolerance of a few percentage points, and in some cases contains fewer mistakes than the manually generated validation data. Through further refinement and generalizing beyond only INHS images, we aim to create a tool that can be distributed to specimen image collection curators to correct the metadata sparsity that precipitated this work.
\subsection{Future Work}
The most pressing next step is to refine the pixel analysis thresholding process so that the entirety of even light colored fish are marked as foreground in the mask. A deficiency of the current process is that it only operates on single channel intensity. Some of the lightest tails appear yellow in hue to the human eye and easily distinguishable, but when compressed to a single intensity value they are almost identical in value to the white background. Considering when the RGB channels of a pixel are not equal in value may be able to improve masking of such features. Another possible approach to solving this is to threshold and mask on subsets of the bounding box, as to ensure that very dark trunk pixels do not affect the thresholding of lighter regions.

@@

%\section*{Acknowledgment}
%can make possible note about larger BGNN team, and/or general note to Tulane data in-putters for giving us data to compare, and/or INHS collection. [we can discuss]
